\begin{thebibliography}{99}
\bibitem{bose}M. H. Anderson et al., Science 269, 198(1995)
\bibitem{fesh}S. Inouye, M. R. Andrews, J. Stenger, H.-J. Miesner, D. M. Stamper-Kurn, and W. Ketterle. Observation of Feshbach resonances in a Bose-Einstein condensate. Nature, 392, pp. 151 – 154, (1998)
\bibitem{efimov}Greene, C. H., Giannakeas, P. and Pérez-Ríos, J. Universal few-body physics and cluster formation. Rev. Mod. Phys. 89, 035006 (2017)
\bibitem{ion-rydberg}Nicolas Zuber, Viraatt S. V. Anasuri, Moritz Berngruber, Yi-Quan Zou, Florian Meinert, Robert Löw and Tilman Pfau "Observation of a molecular bond between ions and Rydberg atoms"  Nature, 605, pp. 453 – 456, (2022)
\bibitem{kobayashi}Jun Kobayashi et al., Nature Comn 10, 3771
\bibitem{okuda}奥田泰崇 「共振器増幅された 3 次元光格子中でのレーザー冷却実験」 北海道大学 2022
\bibitem{rucas}Rucas beguin "Measurement of the van der Waals interaction between two Rydberg atoms" Appendix B, University of Basel 2013
\bibitem{rydberg}T.Gallagher "Rydberg Atoms" Cambridge University Press 2005.
\bibitem{yuma}中村 勇真 「単一イッテルビウム原子を用いた量子計算に向けた光ピンセットアレイシステムの開発とリドベルグ分光」 京都大学大学院　2022
\bibitem{yamamotomasashi} 陳　軍・山本将史 『らくらく図解 光とレーザー』 オーム社 2006
\bibitem{suzuki}鈴木 皓博・井上 慎「光会合用レーザーシステムの開発」 東京大学 2013
\bibitem{foot}C. J. Foot: ”Atomic Physics”, OXFORD UNIVERSITY PRESS (2005)
\bibitem{eit-pertubation}林 暢仁 「ラダー型及び Λ 型 3 準位系における量子干渉効果」 熊本大学大学院 (2011)
\bibitem{eit-absorption}Sumanta Khan, Vineet Bharti, Vasant Natarajan ”Role of dressed-state interference in electromagnetically induced transparency”, Indian Institute of Science (2016)
\bibitem{mt}D. J. McCarron, S. A. King and S. L. Cornish "Modulation transfer spectroscopy in atomic
\bibitem{mt2}池田 幸平 「通信波長帯周波数安定化レーザーと天文コムへの応用」 横浜国立大学大学院 2019
\bibitem{four-wave}矢島 達夫 「非線形光学の基礎II:2次と3次の現象」日本大学 1998
\bibitem{nagaoka-yosuke}長岡 洋介 物理入門コース4 電磁気学$\mathrm{I}\hspace{-1.2pt}\mathrm{I}$ 変動する電磁場 10章
\bibitem{optimize}HSUAN-JUI SU, JIA-YOU LIOU, I-CHUN LIN, AND YI-HSIN CHEN "Optimizing the Rydberg EIT spectrum in a thermal vapor" Vol. 30, No. 2/17 Jan 2022/ Optics Express 1499
\bibitem{takase-y}高瀬 直美 「Rydberg励起用周波数安定化波長420nm半導体レーザーの開発」 電気通信大学 2019
\bibitem{hyperfine}"Hyperfine Structure Measurements of the 85Rb and 87Rb 6P3/2 State" IEEE International Frequency Control Symposium (2019)
\bibitem{1.6}Krishnapriya Subramonian Rajasree, Kristoffer Karlsson, Tridib Ray, and Síle Nic Chormaic "1.6GHz Frequency Scanning of a 482 nm Laser Stabilized Using Electromagnetically Induced Transparency" IEEE PHOTONICS TECHNOLOGY LETTERS, VOL.33, NO.15, AUGUST 1, 2021
\bibitem{quantum-defect}Wenhui Li, I. Mourachko, M. W. Noel, and T. F. Gallagher "Millimeter-wave spectroscopy of cold Rb Rydberg atoms in a magneto-optical trap: Quantum defects of the ns, np, and nd series" University of Virginia, Bryn Mawr College 2003

Quantum defects of the ns, np, and nd series
\bibitem{nist}NIST Atomic Spectra Database Levels Data
\end{thebibliography}